R Notebook

### 2023-11-03 Tensor MSSA.rmd
Fixed

```{r}
LPA.mat <- numeric(iterations)
LPA.tens <- numeric(iterations)
mse.mat <- matrix(0, ncol = iterations, nrow = series.number)
mse.tens <- matrix(0, ncol = iterations, nrow = series.number)

iterations <- 1000
pb <- txtProgressBar(max = iterations, style = 3)
for (i in 1:iterations) {
  # noised case
  s.n <- lapply(s, function(x) x + rnorm(N, sd = sigma))
  # noiseless case
  # s.n <- s
  s.n.hankel <- lapply(s.n, hankel, L)
  mat.n <- reduce(s.n.hankel, cbind)
  u.n.svd <- svd(mat.n)
  est.subspace <- u.n.svd$u[, 1:min(r, N - L + 1), drop = FALSE]
  mat.rec <- reconstruct(ssa(s.n, L = L, kind = "mssa"), groups = list(1:r))[[1]]

>>>>

```{r}
iterations <- 1000
LPA.mat <- numeric(iterations)
LPA.tens <- numeric(iterations)
mse.mat <- matrix(0, ncol = iterations, nrow = series.number)
mse.tens <- matrix(0, ncol = iterations, nrow = series.number)

pb <- txtProgressBar(max = iterations, style = 3)
for (i in 1:iterations) {
  # noised case
  s.n <- lapply(s, function(x) x + rnorm(N, sd = sigma))
  # noiseless case
  # s.n <- s
  s.n.hankel <- lapply(s.n, hankel, L)
  mat.n <- reduce(s.n.hankel, cbind)
  u.n.svd <- svd(mat.n)
  est.subspace <- u.n.svd$u[, 1:min(r, N - L + 1), drop = FALSE]
  mat.rec <- reconstruct(ssa(s.n, L = L, kind = "mssa"), groups = list(1:r))[[1]]
